Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-10 R0V0.tex
Change the set \Xi, introduce new set Y_i and X_i

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 																			   %
% Git Branch: Manchester20160725											   %
% 																			   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
\begin{subequations}
	\begin{equation*}
		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
	\end{equation*}
	and
	\begin{align*}
		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
		\text{has the properties}\ \mathscr{K}_Y(i)\ &\text{and}\ \mathscr{K}(i)\}.
	\end{align*}
\end{subequations}
Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero. By definition, this set is the complement of $\mathscr{K}(i)$. Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$. As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 																			   %
% Git Branch: Master	 													   %
% 																			   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Following the notation introduced in \cite{Tanaka2011}, For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
\begin{subequations}
	\begin{align*}
		\Xi=&\ \{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		&\ \forall j\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, and the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$. The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential}.

It remains to specify the dependence of each component of the matrix $Y$ on the elements of the state-space variable. To that end, let the set
\begin{align*}
		\mathbf{Y}_i=\{Y_{ij}:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ | \arg(Y_{ij})\in\mathbf{X}_i\}\;,
\end{align*}
where the set $\mathbf{X}_i$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(i)$.

Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero. By definition, this set is the complement of $\mathscr{K}(i)$. Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$. As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.
